Learning Features and Abstract Actions for Computing Generalized Plans

### 2018-11-12 doc/camera-ready/paper.tex
Fix typo

The paper is organized as follows. We first provide background and then show 
how an abstract actions can be learned by enforcing soundness and
completeness over a set of samples from a pool of candidate features derived
from the domain predicates. The computational model is then summarized,
followed by experimental results and a discussion.

@@

\medskip
\begin{example}
Let $\Q_{clear}$ stand for  all  Blocksworld instances with stack and unstack actions and goal $clear(x)$,
let $F=\{H,n(x)\}$ be the set of the two features above, and let $s$ be a reachable state in an instance $P$
in $\Q_{clear}$
where the gripper is empty, the atoms $on(A,B)$ and $clear(A)$ are true, and the block $A$ is above $x$.
In this state $s$,
the abstract action $\bar{a}=\abst{\neg H,n(x)>0}{H,n(x)\mminus}$
and the concrete  action  $a=\text{Unstack}(A,B)$ have the same effect over the features.
Indeed, $\bar{a}$ and $a$  are both applicable in $s$, and while $\bar{a}$ makes the variable $H$ true and decreases
$n(x)$, the action $a$ results in a state $s'$ where $\phi_{H}(s')$ is true and $\phi_{n(x)}(s') < \phi_{n(x)}(s)$.
\end{example}

>>>>

The paper is organized as follows. We first provide background and then show 
how abstract actions can be learned by enforcing soundness and
completeness over a set of samples from a pool of candidate features derived
from the domain predicates. The computational model is then summarized,
followed by experimental results and a discussion.

@@

\medskip
\begin{example}
Let $\Q_{clear}$ stand for  all  Blocksworld instances with stack and unstack actions and goal $clear(x)$,
let $F=\{H,n(x)\}$ be the set with the two features above, and let $s$ be a reachable state in an instance $P$
in $\Q_{clear}$
where the gripper is empty, the atoms $on(A,B)$ and $clear(A)$ are true, and the block $A$ is above $x$.
In this state $s$,
the abstract action $\bar{a}=\abst{\neg H,n(x)>0}{H,n(x)\mminus}$
and the concrete  action  $a=\text{Unstack}(A,B)$ have the same effect over the features.
Indeed, $\bar{a}$ and $a$  are both applicable in $s$, and while $\bar{a}$ makes the variable $H$ true and decreases
$n(x)$, the action $a$ results in a state $s'$ where $\phi_{H}(s')$ is true and $\phi_{n(x)}(s') < \phi_{n(x)}(s)$.
\end{example}
